Chronic conditions and increased antibiotic consumption

### 2017-03-14 chronic-conditions/chronic-condition-drivers.Rmd
only lasso

```{r lasso}
library(glmnet)
require(doMC)
registerDoMC(cores=3)

@@

lasso_cv = cv.glmnet(lasso_x, lasso_y, parallel=TRUE, family='poisson')
#lasso_model = glmnet(lasso_x, lasso_y, family='poisson')
```

```{r multivariate_linear_model}
multivariate_formula = paste(c('n_claims ~ age + is_female', conditions), collapse=' + ') %>%
  formula

multivariate_linear_res = usage_summary %>%
  lm(multivariate_formula, data=.) %>%
  tidy

# For multivariate Poisson:
# glm(multivariate_formula, family='poisson', data=.)
```

@@

### Multivariate linear model

I also performed multivariate regressions, keeping all the chronic conditions as well as age and sex (coded as "is female") as explanatory variables.

I don't expect a linear model to work well, since the output is count data, but doing a Poisson regression took a really long time.

```{r cache=FALSE}
multivariate_linear_res %>%
  mutate(pct.increase=round((exp(estimate)-1.0)*100)) %>%
  arrange(desc(pct.increase)) %>%
  kable
```

### Lasso

I also performed a lasso regression with the Poisson model. I started with 10-fold cross-validation to pick the $\lambda$.

>>>>

```{r lasso_poisson}
library(glmnet)
require(doMC)
registerDoMC(cores=3)

@@

lasso_cv = cv.glmnet(lasso_x, lasso_y, parallel=TRUE, family='poisson')
```

@@

### Multivariate lasso

I also performed a multivariate lasso regression with the Poisson model, keeping all the chronic conditions as well as age and sex (coded as "is female") as explanatory variables.
I started with 10-fold cross-validation to pick the lasso $\lambda$.
